---
title: "cheatsheet-r-pkgs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cheatsheet-r-pkgs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(devtools)
library(testthat)
```

## Package setup

At the beginning of a project, run these commands once.  No harm will come if you run them again, but you don't need to unless you want to change something.  

```{r pkg-set-up, eval=FALSE, include=TRUE}
library(devtools)
library(usethis)

# Create a new package
path <- file.path(tempdir(), "mypkg")
create_package(path)

# Modify the description 
use_mit_license("My Name")

# Add packages to use in package
use_package("MASS", "Suggests")

# Set up other files 
use_readme_rmd()
  #to update readme
  build_readme()

# use test-that
use_testthat()

# Use git 
use_git()
```


## Git credentials

Follow the instructions here: https://usethis.r-lib.org/articles/articles/git-credentials.html#practical-instructions-1.  Have a look at the topic on 'scope' in particular.  

```{r git, eval=FALSE, include=TRUE}
# check your settings
gh_token_help()

git_sitrep()

# find and remove legacy credentials in `.Renviron` (`GITHUB_PAT` or `GITHUB_TOKEN`)
usethis::edit_r_environ()

# create a personal access token on github 
usethis::create_github_token()

# enter PAT to local git credentials store
gitcreds::gitcreds_set()
```


## Workflow

Once the package has been set up, the workflow is: 

- create a script  
- creative cycle  
  - edit  
  - write test
  - test  
- load
- commit
- check
- document
- install

```{r workflow, eval=FALSE, include=TRUE}
# create or edit a script
use_r("myscript1")

# adding data for tests
use_data_raw(name = "mydataset") #create script for making dataset

  #example content of data file:  
  x <- 1
  y <- 2

use_data(x, y)

# load
load_all()

# write test
use_test("myscript1") #creates or opens a test file
  #example content of test file: 
  test_that("multiplication works", {
    expect_equal(2 * 2, 4)
  })


# test
test()




```





