---
title: "grreat"
author: "Christoph Kratz"
date: "10/10/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{grreat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(packlearn)
```

## Background

Picture this: you've just eaten some amazing food.  It's so amazing you've lost the ability to express just how amazing it is in words. What do you do?

Well just fire up a computer, start `R`, install this amazing package (using `devtools::install_github("bogsnork/packlearn"))`, load the package with `library(packlearn)` and... **use the `grreat` function** with `grreat(name = "awesome food")` and praise is generated for you!

## Wait, this works with any food??
Yes, any foodstuff you can think of.  The only criterion is that it has a name that you can type.  

## I fid this hard to believe.
It's true

## Prove it!
OK, but hold tight.  

Say you've just eaten beef...

```{r}
grreat(food = "beef")
```

Then you had some pie...

```{r}
grreat(food = "pie")
```

## But I'm vegetarian!
I'm not finished ...

```{r}
grreat(food = "vegetarian pie")
```

## I'm gluten intolerant
We have *catered* for that ;-)

```{r}
grreat(food = "rice")
```

## What if I want to praise a drink, a piece of art, a person??
Regrettably that functionality has not been enabled in the current version of the package.  

